### 2019-02-27 sections/example.tex
new paragraph after itemize in example

The requirements of the application are as follows.
\begin{enumerate*}
  \item A user has to enter a list of passengers for which to book tickets.
  \item At least one of these passengers has to be an adult.
  \item After a valid list of passengers has been entered, the user has to pick seats.
  \item Only free seats may be picked.
  \item Every passenger must have exactly one seat.
  \item Multiple users should be able to book tickets at the same time.
\end{enumerate*}
For this example we assume that the host language has lists and four functions on them: all, any, intersect, and difference.
The functions all and any check if all or any elements in a list satisfy a given predicate.
The functions intersect and difference compute the set-intersection and set-difference of two lists.
%%NOTE: After Peter's comments symbols are not clear --TS
We also make use of string equality ($\equiv$), dereferencing ($!$), reference assignment ($:=$), and expression sequencing ($;$).
For brevity, we omit the type annotations of variable bindings.

>>>>

The requirements of the application are as follows.
\begin{enumerate*}
  \item A user has to enter a list of passengers for which to book tickets.
  \item At least one of these passengers has to be an adult.
  \item After a valid list of passengers has been entered, the user has to pick seats.
  \item Only free seats may be picked.
  \item Every passenger must have exactly one seat.
  \item Multiple users should be able to book tickets at the same time.
\end{enumerate*}

For this example we assume that the host language has lists and four functions on them: \TS{all}, \TS{any}, \TS{intersect}, and \TS{difference}.
The functions \TS{all} and \TS{any} check if all or any elements in a list satisfy a given predicate.
The functions \TS{intersect} and \TS{difference} compute the set-intersection and set-difference of two lists.
%%NOTE: After Peter's comments symbols are not clear --TS
We also make use of string equality ($\equiv$), dereferencing ($!$), reference assignment ($:=$), and expression sequencing ($;$).
For brevity, we omit the type annotations of variable bindings.
